---
title: "An_Interview_Test"
output: html_document
date: '2022-04-26'
---

```{r}
library(readr)
library(tidyverse)
library(broom)
library(ggpubr)
```

```{r}
grades_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/grades.csv'
assignments_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/assignments.csv' 
students_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/students.csv'
grades_df = read_csv(url(grades_url))
assignments_df = read_csv(url(assignments_url))
students_df = read_csv(url(students_url))
```

#Question 1:
There are 180 students with not duplicates because each student has their own unique ID.

#Question 2: 
There are six distinct majors, with the amount distribution as follows:
  Business: 27
  Engineering: 52
  English: 30
  Philosophy: 30
  Science: 21
  Statistics and Math: 20

```{r}
table(students_df$major)
```


#Question 3:

```{r}
table(students_df$major, students_df$student_level)
```
                      Freshmen   Sophomore   Junior   Senior
Business                     9          11        3        4
Engineering                 24          14       14        0
English                     11           8        5        6
Philosophy                  14           7        8        1
Science                      8           6        5        2
Statistics and Math          6           9        2        3

#Question 4: Senior engineers have the lowest number of students, having zero students enrolled.

#Question 5:

```{r}
ggplot(students_df, aes(y = fct_rev(fct_infreq(major)))) + 
  geom_bar(fill = "#F57251") + 
  labs(title = "Number of Students in Each Major", x = "Amount of Students", y = "Majors") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```


#Question 6:

```{r}

mod_students_df = students_df %>%
  mutate(student_grade = gsub(".*-", "", student_level))

ggplot(mod_students_df, aes(y = major, fill = student_grade)) +
  geom_bar() + 
  scale_fill_manual(values=c("#7BA88A", "#E67D65", "#65A2E6", "#FEDA70")) + 
  labs(title = "Number of Students in Each Major", x = "Amount of Students", y = "Majors") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5))


```

#Question 7

```{r}
student_grades_df = merge(x=students_df, y=grades_df)
```

#Question 8
Student ID 288941 performed the worst on asignment 1 as an English major.


#Question 9

```{r}
average_junior_student_grades_df = student_grades_df %>% 
  filter(student_level == '3-Junior') %>% 
  group_by(assignment_id) %>% 
  summarise_at(vars(numeric_grade), list(grade = mean)) %>% 
  ungroup()
```

Assignment number 10 had the highest average grade.

#Question 10

```{r}
average_math_student_grades_df = student_grades_df %>% 
  filter(major == 'Statistics and Math') %>% 
  group_by(student_level) %>% 
  summarise_at(vars(numeric_grade), list(average_grade = mean))
```

The sophomores had the highest average at 17.63333.

#Question 11
```{r}
gradebook_df = merge(student_grades_df, assignments_df)
```

#Question 12
```{r}
exam_gradebook_df = gradebook_df %>% 
  filter(assignment_category == 'Exam') %>% 
  mutate(student_level = gsub(".*-", "", student_level)) %>% 
  mutate(Major = major)

exam_gradebook_df %>% 
  ggplot(aes(x=Major, y=numeric_grade, fill = Major)) + 
  geom_bar(stat = "identity") +
  ylim(0,100) +
  facet_grid(cols = vars(student_level)) +
  scale_x_discrete(labels = element_blank()) +
    labs(title = "Number of Students in Each Major", x = "Grade Level", y = "Average Exam Grade") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5), strip.text.x = element_text(size = 8))
```
#Question 13

a. 
```{r}
exam_2_freshman_df = gradebook_df %>% 
  filter(assignment_category == 'Exam') %>% 
  filter(assignment_id == "20") %>% 
  filter(student_level == "1-Freshmen")
  
```


b.
Explanatory Variable: major
Response Variable: exam grade

c.
Null hypothesis: There is no significant difference between freshman exam grades based off major.
Alternative hypothesis: There is a significant difference between freshman with different majors and their average exam grades.

d.
```{r}
summary_exam_df = exam_2_freshman_df %>% 
  group_by(major) %>% 
  summarise(sample_size = n(),
            mean_grade = mean(numeric_grade,na.rm = TRUE),
            sd_grade = sd(numeric_grade,na.rm = TRUE))

summary_exam_df
```

```{r}
exam_2_freshman_df %>% 
  ggplot(aes(x = major, y = numeric_grade)) +
  geom_boxplot() +
  stat_summary(fun ="mean", color = 'blue')+
  labs(x = 'Major', y = 'Grade', title = 'Box Plot for One-Way ANOVA') +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 15))
```



e. Since there is an observable difference between exam scores based on different majors we can reject the null hypothesis and accept the alternative.


#Question 14

a.
```{r}
mod_exam_df = gradebook_df %>% 
    mutate(assignment_id = as.factor(assignment_id)) %>% 
  filter(assignment_category == 'Exam')

```


b.
Explanatory Variables: major and assignment_id 
Response Variable: exam grade

c.
Null hypothesis: There is no significant difference between freshman exam grades based off major or the different exams.
Alternative hypothesis: There is a significant difference between freshman with different majors on the different exams and their average exam grades.

d.
```{r}
summary_mod_exam_df = mod_exam_df %>% 
  group_by(major, assignment_id) %>% 
  summarise(sample_size = n(),
            mean_grade = mean(numeric_grade,na.rm = TRUE),
            sd_grade = sd(numeric_grade,na.rm = TRUE))

summary_exam_df
```

```{r}
ggboxplot(mod_exam_df, x = "major", y = "numeric_grade", color = "assignment_id",
          palette = c("#00AFBB", "#E7B800")) +
  labs(x = 'Major', y = 'Grade', title = 'Average Test Grade of Two Exams Based on Major') +
  theme(plot.title = element_text(hjust = 0.5, face = 'bold', size = 12), axis.text=element_text(size=7))
```


e. 
Since there is a significant difference between different majors and different exams, we can reject the null hypothesis.




