---
title: "An_Interview_Test"
output: html_document
date: '2022-04-26'
---

```{r}
library(readr)
library(tidyverse)
```

```{r}
grades_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/grades.csv'
assignments_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/assignments.csv' 
students_url = 'https://raw.githubusercontent.com/gato365/emandoesgato365/main/content/post/2022-04-25-an-interview-test/students.csv'
grades_df = read_csv(url(grades_url))
assignments_df = read_csv(url(assignments_url))
students_df = read_csv(url(students_url))
```

#Question 1:
There are 180 students with not duplicates because each student has their own unique ID.

#Question 2: 
There are six distinct majors, with the amount distribution as follows:
  Business: 27
  Engineering: 52
  English: 30
  Philosophy: 30
  Science: 21
  Statistics and Math: 20

```{r}
table(students_df$major)
```


#Question 3:

```{r}
table(students_df$major, students_df$student_level)
```
                      Freshmen   Sophomore   Junior   Senior
Business                     9          11        3        4
Engineering                 24          14       14        0
English                     11           8        5        6
Philosophy                  14           7        8        1
Science                      8           6        5        2
Statistics and Math          6           9        2        3

#Question 4: Senior engineers have the lowest number of students, having zero students enrolled.

#Question 5:


```{r}
ggplot(students_df, aes(y = fct_rev(fct_infreq(major)))) + 
  geom_bar(fill = "#F57251") + 
  labs(title = "Number of Students in Each Major", x = "Amount of Students", y = "Majors") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```


#Question 6:

```{r}

mod_students_df = students_df %>%
  mutate(student_grade = gsub(".*-", "", student_level))

ggplot(mod_students_df, aes(y = major, fill = student_grade)) +
  geom_bar() + 
  scale_fill_manual(values=c("#7BA88A", "#E67D65", "#65A2E6", "#FEDA70")) + 
  labs(title = "Number of Students in Each Major", x = "Amount of Students", y = "Majors") +
  theme_gray() + 
  theme(plot.title = element_text(hjust = 0.5))


```
